Species persistence under climate and fishing

### 2014-01-29 Writing/plots/figureCode/compareCatch.Rmd
Looking at how catch varies, #13

Trying the same plot but a higher rate of catch: $h = 0.10$ I get,

@@

>>>>

Trying the same plot but a higher rate of catch: $$h = 0.10$$ I get,

@@

Looking at holding speed constant and examining catch as a function of harvest

```{r harvestVar, echo = FALSE, fig.width=10, fig.height=5}
subData <- subset(allData,speed==0.1)
ggplot(subData, aes(x = harvest, y = Equil.harvest)) + facet_wrap(~management) + geom_line() + geom_ribbon(aes(ymin = Equil.harvest - Equil.harvest.se, ymax = Equil.harvest + Equil.harvest.se), alpha = 0.35) + theme_bw()

subData <- subset(allData,speed==0.2)
ggplot(subData, aes(x = harvest, y = Equil.harvest)) + facet_wrap(~management) + geom_line() + geom_ribbon(aes(ymin = Equil.harvest - Equil.harvest.se, ymax = Equil.harvest + Equil.harvest.se), alpha = 0.35) + theme_bw()

subData <- subset(allData,speed==0.3)
ggplot(subData, aes(x = harvest, y = Equil.harvest)) + facet_wrap(~management) + geom_line() + geom_ribbon(aes(ymin = Equil.harvest - Equil.harvest.se, ymax = Equil.harvest + Equil.harvest.se), alpha = 0.35) + theme_bw()
```
